---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

# Ole Ivar Rudi's CRT scanline method

## Intro
* I stumbled upon Ole's [original tweet](https://twitter.com/oleivarrudi/status/895665025251123201?s=20) and thought it looked super cool!
* So here is my (hopefully accurate) recreation of it using the [ImageMagick STL](https://www.imagemagick.org/Magick++/STL.html) through the R `{magick}` package
  * I'm not sure if all details are exactly the same - but I'm really happy with the output this produces
* AS Ole says

> Of course, this is a completely technically wrong and unscientific way of doing it, but it gets the iidea across far better than the industry standard way of just adding black lines for every second vertical pixel, which darkens the image too much imo

## Read original image
* Read a SNES image at its original resolution (256w x 224h pixels)

```{r warning = FALSE, message = FALSE}
library(magick)

original <- image_read('original.png')
original
```

## Rescale image
* Extract the width and height as variables
* Then scale the image in two steps
  1. Scale 4x vertically using the `point` filter ([which I believe is the same as 'nearest neighbour'?](https://legacy.imagemagick.org/Usage/filter/#point))
  2. Scale 4x horizontally using the `triangle` filter ([which I believe is similar to bilinear?](https://legacy.imagemagick.org/Usage/filter/#triangle)) *to replicate that CRT scanline horizontal smudge feel*
```{r}
w <- image_info(original)$width
h <- image_info(original)$height

original_scaled <-
    image_resize(original, geometry = paste0(w, 'x', h*4, '!'), filter = "point") |> 
    image_resize(geometry = paste0(w*4, 'x', h*4, '!'), filter = "triangle")

original_scaled
```

## Create scanline pattern
* As per Ole's recipe, I create a 4 pixel height scanline pattern
  * *2 clear pixels, one half transparent pixel and one black pixel*

```{r}
x <- c(
    rgb(255, 255, 255, 000, maxColorValue = 255), # 100% transparent white
    rgb(255, 255, 255, 000, maxColorValue = 255), # 100% transparent white
    rgb(000, 000, 000, 128, maxColorValue = 255), # 50% transparent black
    rgb(000, 000, 000, 255, maxColorValue = 255)  # opaque black
    )

sl_filter <-
    rep(x, length.out = h*4) |> 
    rep(each = w*4) |> 
    matrix(ncol = w*4, nrow = h*4, byrow = TRUE) |> 
    image_read()
```

## Layer the scanline pattern
* Then layer the scanline pattern using the `SoftLight` operator
```{r}
out <- image_composite(original_scaled, sl_filter, operator = "SoftLight")
out
```

## Inspect output
```{r warning = FALSE, message = FALSE, fig.width = 9, fig.height = 4, dpi=600}
library(tidyverse)
x_zoom <- c(700, 800)
y_zoom <- c(200, 300)

# Scale the original 4x using point in both x and y
# This is to get the original to match the two outputs in pixel dimensions
original |> 
    image_resize("400%", filter = "point") |> 
    image_flip() |> 
    image_raster() |> 
    mutate(type = '1. Original (scaled 4x)') |> 
    filter(
        between(x, x_zoom[1], x_zoom[2]),
        between(y, y_zoom[1], y_zoom[2])) |> 
    # Bind rows to original with separate scaling in y and x
    bind_rows(
        original_scaled |> 
            image_flip() |> 
            image_raster() |>
            mutate(type = "2. Horizontal 'smudge scaled' \n (Vertical: Nearest Neighbour) \n (Horizontal: Bilinear)") |> 
            filter(
                between(x, x_zoom[1], x_zoom[2]),
                between(y, y_zoom[1], y_zoom[2]))) |> 
    # Bind rows to original with separate scaling in y and x and scanline filter applied
    bind_rows(
        out |> 
            image_flip() |> 
            image_raster() |>
            mutate(type = '3. Scanline filter (4 pixel height) applied') |> 
            filter(
                between(x, x_zoom[1], x_zoom[2]),
                between(y, y_zoom[1], y_zoom[2])))|> 
    ggplot() + 
    geom_raster(aes(x, y, fill=I(col)))+
    coord_equal() +
    facet_wrap(~type)
```


## Save outputs
* Save the output at full resolution
```{r}
image_write(original_scaled, 'original_scaled.png')
image_write(out, 'original_scanlined.png')
```

## Extending to 6 pixel height symmetric scanline filter
* With even more horizontal smudge by using a `cubic` filter
```{r}
original_scaled_6x <-
    image_resize(original, geometry = paste0(w, 'x', h*6, '!'), filter = "point") |> 
    image_resize(geometry = paste0(w*6, 'x', h*6, '!'), filter = "cubic")

x <- c(
    rgb(000, 000, 000, 255, maxColorValue = 255), # opaque black
    rgb(000, 000, 000, 128, maxColorValue = 255), # 50% transparent black
    rgb(255, 255, 255, 000, maxColorValue = 255), # 100% transparent white
    rgb(255, 255, 255, 000, maxColorValue = 255), # 100% transparent white
    rgb(000, 000, 000, 128, maxColorValue = 255), # 50% transparent black
    rgb(000, 000, 000, 255, maxColorValue = 255)  # opaque black
    )

sl_filter_6x <-
    rep(x, length.out = h*6) |> 
    rep(each = w*6) |> 
    matrix(ncol = w*6, nrow = h*6, byrow = TRUE) |> 
    image_read()

out_6x <- image_composite(original_scaled_6x, sl_filter_6x, operator = "SoftLight")
out_6x
```

* Inspect output
```{r fig.width = 9, fig.height = 4, dpi=600}
# Recompute the zoom coords for the 6x scaled image
x_zoom <- x_zoom*1.5
y_zoom <- y_zoom*1.5

# Scale the original 6x using point in both x and y
# This is to get the original to match the two outputs in pixel dimensions
original |> 
    image_resize("600%", filter = "point") |> 
    image_flip() |> 
    image_raster() |> 
    mutate(type = '1. Original (scaled 6x)') |> 
    filter(
        between(x, x_zoom[1], x_zoom[2]),
        between(y, y_zoom[1], y_zoom[2])) |> 
    # Bind rows to original with separate scaling in y and x
    bind_rows(
        original_scaled_6x |> 
            image_flip() |> 
            image_raster() |>
            mutate(type = "2. Horizontal 'smudge scaled' \n (Vertical: Nearest Neighbour) \n (Horizontal: Cubic)") |> 
            filter(
                between(x, x_zoom[1], x_zoom[2]),
                between(y, y_zoom[1], y_zoom[2]))) |> 
    # Bind rows to original with separate scaling in y and x and scanline filter applied
    bind_rows(
        out_6x |> 
            image_flip() |> 
            image_raster() |>
            mutate(type = '3. Scanline filter (6 pixel height) applied') |> 
            filter(
                between(x, x_zoom[1], x_zoom[2]),
                between(y, y_zoom[1], y_zoom[2])))|> 
    ggplot() + 
    geom_raster(aes(x, y, fill=I(col)))+
    coord_equal() +
    facet_wrap(~type)
```

* Save the 6x outputs at full resolution
```{r}
image_write(original_scaled_6x, 'original_scaled_6x.png')
image_write(out_6x, 'original_scanlined_6x.png')
```


